Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
add changes

\paragraph*{Symmetric Lenses}
A classical symmetric lens
$\Lens$ between $X$ and $Y$ consists of 4 components: a complement $C$, a
designated element $init \in C$, and two functions,
$\PutRSym$ and $\PutLSym$, that propagate changes in one format to the other.
\begin{enumerate}
\item $\PutRSym \OfType X \times C \rightarrow Y \times C$
\item $\PutLSym \OfType Y \times C \rightarrow X \times C$
\end{enumerate}
In this formulation, data unique to each side are stored in the complement.
When one format is edited, the \PutR
or \PutL function stitches together the edited data with data
stored in the complement.  The  $init$ element is used as the
initial value of $C$ and specifies default behavior when data is missing.
For instance, to implement the
scenario in Figure~\ref{fig:minimized-representations}, the complement
would consist of a list of pairs of salary and company name.

Classical symmetric lenses satisfy the following equational laws.
\begin{equation}
  \tag{\PutRL}
  \frac{\PutRSymOf{(x,c)} = (y,c'')}{\PutLSymOf{(y,c'''')} = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutLSymOf{(y,c)} = (x,c')}{\PutRSymOf{(x,c'')} = (y,c')}
\end{equation}

>>>>

\paragraph*{Symmetric Lenses}
A classical symmetric lens $\Lens$ between $X$ and $Y$ consists of 4 components:
a complement $C$, a designated element $init \in C$, and two functions,
$\PutRSym \OfType X \times C \rightarrow Y \times C$ and $\PutLSym \OfType Y
\times C \rightarrow X \times C$, that propagate changes in one format to the
other.

In this formulation, data unique to each side are stored in the complement. When
one format is edited, the \PutR or \PutL function stitches together the edited
data with data stored in the complement. The $init$ element is the initial value
of $C$ and specifies default behavior when data is missing. For instance, to
implement the scenario in Figure~\ref{fig:minimized-representations}, the
complement would consist of a list of pairs of salary and company name.
Classical symmetric lenses satisfy the following equational laws.
\begin{equation}
  \tag{\PutRL}
  \frac{\PutRSymOf{(x,c)} = (y,c'')}{\PutLSymOf{(y,c'''')} = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutLSymOf{(y,c)} = (x,c')}{\PutRSymOf{(x,c'')} = (y,c')}
\end{equation}
